\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex
part of badusb.tex; not finish.

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking USB device as highly
dangerous and be cautious about them. These assumptions are approved in a
relevant work about charging attack~\cite{JFCImpact}. Moreover, we neglect the
effect of notification about common USB device, as normal users usually are not
equipped with the necessary knowledge to fully understand such notices. In
fact, during our experiment, no device had security notifications raised about
suspicious USB devices and only mobile devices had raised charging notification
about our \tool, which may not be a sufficient warning towards users.

We also assume the victim's device is equipped with fully functional USB 3.x
protocol and USB Type C connector. As the USB 3.x standard is more and more
common nowadays, this assumption can be easily fulfilled especially in recent
devices.

@@

\subsection{Implementation}
%\noindent\hongyi{The following mode is to be further decided}\\
%\outline{DETAIL of each mode}\\ \outline{Automatic Scripting Mode}\\
%\outline{Remote Control Mode}\\ \outline{OCR/QR Recognition Mode}\\
As we introduced in Section~\ref{sec:related_work}, there are plenty of
existing work~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focusing on BadUSB attack.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal HID devices and utilize USB protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as HIDs (like keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to lack of user interface (UI).  Whatever HID the
attackers simulate their USB devices to be, they could not obtain the UI to
check the current situation, which makes it nearly impossible to carry out
their attacks precisely or confirm the effects after attacks.

In this work, we utilized the new features of USB 3.x~\cite{usb31,usb32} to
address the problems above.  Benefiting from latest protocol, we simulated
external display and thus obtained the video stream to perform accurate
attacks.

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited. 
Based on the drawbacks introduced above, several defense mechanisms were
proposed, like GoodUSB~\cite{tian2015defending}. These defense mechanism
implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
complete certain challenges when an unknown HID device is plugged in. As the
BadUSB is only able to emulate a limited kind of devices like HID or disks, by
no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of
bypassing this type of defense. Taking advantage of USB 3.x~\cite{usb31,usb32},
\tool can fetch the video stream of the victim and complete the challenge
manually by the attacker. Moreover, with video capability combined with
traditional BadUSB, our \tool achieved multiple new attack paradigms and are
tested under various real-world scenarios.

As there were various BadUSB implementations available, we only focus on its
core functionality and our extension. In this section, we first introduce the
components we used in \tool, then we focus on the three different attack modes
we implement for various scenarios.

@@

The components in our attack model are as follows, and the relation between
them is illustrated at Figure~\ref{fig:attack_model}. \fengwei{We need to
explain the figure. What are the boxes? Where is victim? Where is the attacker?
The list below only shows the internal components in the malicious USB device.
We might also consider to explain this in the Figure caption.}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}%\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}

>>>>

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking USB device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
effect of notifications from USB devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious USB devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

We also assume the victim's device is equipped with fully functional USB 3.x
protocol and USB Type-C connector. As the USB 3.x standard is
common nowadays, this assumption can be easily fulfilled especially in recent
devices.

@@

\subsection{Implementation}
%\noindent\hongyi{The following mode is to be further decided}\\
%\outline{DETAIL of each mode}\\ \outline{Automatic Scripting Mode}\\
%\outline{Remote Control Mode}\\ \outline{OCR/QR Recognition Mode}\\

As introduced in Section~\ref{sec:related_work}, 
existing works~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal HID devices and utilize USB protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as HIDs (like keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to lack of user interface (UI) status. Whatever HID the
attackers simulate their USB devices to be, they could not obtain the UI to
check the status information, which makes it nearly impossible to carry out
their attacks precisely or know the effects after attacks.

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited.
Based on the drawbacks introduced above, several defense mechanisms were
proposed. GoodUSB~\cite{tian2015defending}
implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
complete certain challenges when an unknown HID device is plugged in. As the
BadUSB is only able to emulate a limited kind of devices such as HIDs or disks, by
no means the BadUSB can bypass it.

In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
address the problem above.  Benefiting from the latest protocol, we simulate
external display and thus obtain the video stream to perform accurate
attacks.
Thus, our \tool is capable of
bypassing defenses such as GoodUSB. Taking advantage of USB 3.x~\cite{usb31,usb32},
\tool can fetch the video stream of the victim and complete the challenge
manually by the attacker. Moreover, with video capability combined with
traditional BadUSB, our \tool achieved multiple new attack paradigms and are
tested under various real-world scenarios.

As there were various BadUSB implementations available, this work focuses on our new extensions. Next, we first introduce the
components we used in \tool, then we focus on the three different attack modes
we implement for various scenarios.

@@

Figure~\ref{fig:attack_model} shows the architecture of our attack model. \mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC. The details of each component in \tool are as follows.\mycircled{1}

%\fengwei{We need to
%explain the figure. What are the boxes? Where is victim? Where is the attacker?
%The list below only shows the internal components in the malicious USB device.
%We might also consider to explain this in the Figure caption.}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/attack_model.png}

	\begin{tabular}{ll}
	\mycircled{1} Victim's Devices    &\mycircled{2}\tool\\
	\mycircled{3} Attacker's Remote PC
	\end{tabular}

	\caption{Attack Model}%\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
